GEE models

### 2017-09-29 doc/manuscript.Rmd
after to over

In a Canadian population of adults who were at-risk for diabetes, we found that 
higher total NEFA concentrations independently predicted lower beta-cell
function after 6 years. While we found negative associations with palmitic acid
(16:0), oleic acid (18:1n-9), and linoleic acid (18:2n-6) for the concentration
(nmol/mL) modeling, no associations were seen for these fatty acids as a
proportion, an observation that was further confirmed by multivariate cluster
techniques, which found no ability of these individual NEFA to predict beta-cell
function. We did find that one fatty acid as a mol%, eicosapentaenoic acid
(20:5n-3), had a positive association with insulin sensitivity. In general,
these observations suggest that the absolute size of the total NEFA fraction,
rather than its specific composition (aside from EPA), likely influences the 
pathogenesis of diabetes, at least within a population at-risk for diabetes.

>>>>

In a Canadian population of adults who were at-risk for diabetes, we found that 
higher total NEFA concentrations independently predicted lower beta-cell
function over 6 years. While we found negative associations with palmitic acid
(16:0), oleic acid (18:1n-9), and linoleic acid (18:2n-6) for the concentration
(nmol/mL) modeling, no associations were seen for these fatty acids as a
proportion, an observation that was further confirmed by multivariate cluster
techniques, which found no ability of these individual NEFA to predict beta-cell
function. We did find that one fatty acid as a mol%, eicosapentaenoic acid
(20:5n-3), had a positive association with insulin sensitivity. In general,
these observations suggest that the absolute size of the total NEFA fraction,
rather than its specific composition (aside from EPA), likely influences the 
pathogenesis of diabetes, at least within a population at-risk for diabetes.
